---
title: "HW1"
author: "JACK PLASTERER"
date: "April 4, 2017"
output:
  html_document: default
  pdf_document: default
---
Link:![](https://www.quora.com/Should-the-USA-implement-single-payer-universal-health-care)

1a.The data visualized are the various countries throughout the world, most of which have a single-payer healthcare system, and the United States, which has a for-profit healthcare program.
1b.This data came from PBS 
2.The data dimensions of each country are represented as blue bars of varying lengths, that is depending on how much each country spends on healthcare as a share of GDP. Light blue indicates how much each country spends privatley while dark blue indicates how much is spent publicly. 
3.This shapes my understanding of the data as it conveys to me which countries are investing in public health care.Moreover, it shows the countries that acutally value health care as a right, and why we (the US) should move in that direction.
4.Something this visualization does well is depict the curve of how much each country pays per capita on healthcare (No surprise the US has the tallest bar). 
5. I would change the visualization by adding more colors to the field for each country in question to better show which countries are spending more publicly on healthcare. 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown



## Including Plots
```
```{r}
```